\documentclass[runningheads]{llncs}

\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\usepackage{booktabs}
\usepackage{array}
\usepackage{listings}
\usepackage{tikz}\usetikzlibrary{positioning}
\usepackage{xcolor}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{[TODO: #1]}}}

\renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{xcolor}

\begin{document}

\title{LACK: A Knowledge Graph of Actors and Relationships Involved in Lobbying Against Climate Knowledge}

\author{Enrico Daga\inst{1} \and
Monika Mačiulienė\inst{2} \and
Arianna Graciotti\inst{3} \and
Jason Carvalho\inst{1} \and
Gregoire Burel\inst{1} \and
Harith Alani\inst{1} }

\authorrunning{E. Daga et al.}

\institute{Knowledge Media Institute, The Open University, Milton Keynes, UK \\
\email{\{enrico.daga, jason.carvalho, gregoire.burel, harith.alani\}@open.ac.uk}}
\institute{ Kaunas University of Technology, ... \\ \email{monika.maciuliene@ktu.lt}}
\institute{ University of Groningen, ... \\ \email{}}

\maketitle
% PLACEHOLDER: Resource links block (required by submission format)
% Resource type: Knowledge Graph and Ontology
% License: CC BY 4.0
% DOI: [to be assigned]
% URL: https://climatesense-project.eu/lack/

\begin{abstract}
Organised lobbying against climate science is extensively documented by investigative platforms such as DeSmog and LobbyMap, yet the information they produce remains fragmented, heterogeneous, and difficult to analyse at scale.
We present LACK (Lobbying Against Climate Knowledge), a knowledge graph of approximately 70,000 typed, temporally annotated relations between persons and organisations involved in climate lobbying, constructed from these sources and linked to Wikidata.
LACK is described using a purpose-built OWL ontology, built via an LLM-based relation extraction pipeline, and published as Linked Open Data under CC BY 4.0 following FAIR principles.
We demonstrate its analytical potential through a use case and validate its utility with domain experts from the investigative journalism and climate accountability sector.

\keywords{Knowledge Graph \and Climate Lobbying \and Relation Extraction \and Ontology \and Linked Data \and FAIR Data}
\end{abstract}


% Resource links (required by submission format)
\noindent\textbf{Resource type:} Knowledge Graph\\
\textbf{License:} Creative Commons Attribution 4.0 International (CC BY 4.0) ---
\url{https://creativecommons.org/licenses/by/4.0/}\\
\textbf{DOI: 10.5281/zenodo.19846036}\\
\textbf{URL:} \url{https://climatesense-project.eu/lack/}

%-----------------------------------------------------------------------

\input{sections/introduction}
\input{sections/related}
\input{sections/extraction}
\input{sections/ontology}
\input{sections/construction}
\input{sections/resource}
\input{sections/usecase}
\input{sections/evaluation}
\input{sections/conclusion}

%-----------------------------------------------------------------------

\paragraph{Supplemental Material.}
The LACK ontology and knowledge graph dump are available at: \url{https://zenodo.org/records/19846036}.
The resource is published under a Creative Commons Attribution 4.0 International (CC BY 4.0) licence.

\clearpage
\section*{Declaration of use of Generative AI}

Claude (Anthropic) was utilised to generate sections of this work including paper structure, drafted text (subsequently substantially revised by the authors), tables, figures, and code. Gemini (Google) was utilised in the knowledge extraction pipeline as a prompt API with tool use, including URL fetching. Groq was utilised as an API with a LLaMA backend in the entity linking pipeline. No generative AI tool is listed as an author.
\bibliographystyle{splncs04}
\bibliography{main}

\end{document}
