\section{Evaluation}
\label{sec:evaluation}

\subsection{Knowledge Acquisition: quality control and error analysis}
\paragraph{Sources} Our collection covers the DeSmog Climate Disinformation Database and the LobbyMap Scores leaderboard in their entirety as of the time of collection, providing complete coverage with respect to these two curated entry points.
With respect to DeSmog, the CDD represents the most systematically curated subset of the broader DeSmog site; other DeSmog databases — covering agribusiness, advertising and PR, and the Koch Network — are relevant to the climate lobbying ecosystem but fall outside the current scope and are left for future work.
With respect to LobbyMap, the Scores leaderboard covers approximately 1,000 companies and 330 industry associations, but InfluenceMap hosts a broader set of content — including sector-level reports, country profiles, and policy engagement assessments — that was not included in the current collection.
Extending coverage to these additional sources remains an important direction for future work.
\paragraph{Relations}

Relation extraction was evaluated on a sample of 300 relations drawn from 8 DeSmog profile pages.
Three annotators (the authors) worked in pairs, each pair covering approximately 100 relations, with disagreements resolved by discussion.
Each relation was assessed on three dimensions: truthfulness (is the relation supported by the source page?), validity (is the relation type and its domain and range correctly applied according to the schema?), and temporal correctness (are the temporal annotations accurate?).

Truthfulness accuracy is 0.93 (0.99 with partial credit), validity 0.907 (0.95 with partial), and temporal correctness 0.797 (0.91 with partial), where partial credit captures approximately correct extractions.

The main source of truthfulness errors is the conflation of specific sub-roles with the coarser schema relations: the model frequently uses \texttt{is president of} or \texttt{is director of} where the source text indicates a more specific role such as vice-president, deputy director, or departmental director.
These cases will be addressed during ontology refinement and KG construction, where finer-grained role distinctions can be introduced.
A recurrent validity issue is the misapplication of organisation-level relations to person-organisation pairs: for example, \texttt{has partner} was used when a person holds a partner title at a law or consulting firm, whereas the relation was intended to connect two organisations in a formal partnership.
This reflects an ambiguity in the original relation schema that has since been refined.
Temporal correctness is the weakest dimension, with errors arising from missing dates, incorrect inference of date ranges, and ambiguity in encoding point-in-time vs.\ interval information.

This evaluation covers DeSmog extractions only, which we acknowledge as a limitation.
LobbyMap was not formally evaluated; however, an informal review of a sample of LobbyMap extractions — whose pages share the same HTML structure and similar tabular layout as DeSmog profiles — suggested comparable extraction quality.

\paragraph{Entities}

Entity linking was evaluated on a sample of 225 entities annotated by four annotators (the authors), each covering approximately 56 entities, with a subset supervised by a second annotator and disagreements resolved by discussion.
Each entity was assessed on five dimensions: entity subtype correctness, Wikidata URI, Wikipedia URL, parent entity, and web page (where applicable); see-also links were assessed separately.

Entity subtype accuracy is 0.951, Wikidata URI 0.920, Wikipedia URL 0.909, and web page 0.938, indicating that the pipeline reliably identifies and links entities across all primary output fields.
Parent entity is the weakest dimension at 0.718; errors appear in part to stem from cases where the pipeline assigned a stock exchange as the parent organisation of publicly listed companies, an artefact of how Wikidata encodes P749/P361 relations.
See-also links achieved perfect accuracy across all annotators.
Of the 275 entities with see-also content, 25 included at least one novel URL beyond the evidence link, contributing 55 additional reference pages in total.

As with the relation evaluation, this assessment covers DeSmog entities only, which we acknowledge as a limitation.

\subsection{Resource Coverage}

\paragraph{Rationale} Resource coverage is evaluated by assessing the extent to which the knowledge graph can answer the competency questions used to drive its design. For each competency question, we identify the ontology relation(s) required to answer it, count the number of triples available for those relations in the KG before and after inferencing, and derive a qualitative coverage estimate. This allows us to assess both the intrinsic density of the extracted data and the contribution of OWL inferencing to query answerability.

%\subsubsection{Research Questions and Competency Questions}

\paragraph{Questions}The following table maps each research question to the competency question(s) it corresponds to, and to the ontology relation(s) required to answer it.

\begin{table}[h]
\centering
\caption{Mapping of research questions to competency questions and ontology relations.}
\label{tab:rq-cq-mapping}
\begin{tabular}{p{0.5\textwidth} p{0.1\textwidth} >{\raggedright}p{0.35\textwidth}}
\hline
\textbf{RQ} & \textbf{CQ} & \textbf{Relation(s)} \tabularnewline
\hline
Who is involved in lobbying against climate science or policy? & CQ1 & \texttt{lack:Person}, \texttt{lack:Collective} (entity enumeration) \tabularnewline
How are lobbying actors funded? & CQ2 & \texttt{lack:fundedBy} / \texttt{lack:hasFunder} \tabularnewline
Who are the members of a given lobbying network? & CQ3 & \texttt{lack:memberOf} / \texttt{lack:hasMember} \tabularnewline
Who leads lobbying organisations? & CQ4 & \texttt{lack:leadsAt} / \texttt{lack:hasLeader} \tabularnewline
What is the employment history of key actors? & CQ5 & \texttt{lack:employedBy} / \texttt{lack:hasEmployee} \tabularnewline
How are organisations structurally connected? & CQ6 & \texttt{lack:hasPartner}, \texttt{lack:sponsored} \tabularnewline
Who founded a lobbying group? & CQ7 & \texttt{lack:founded} / \texttt{lack:wasFoundedBy} \tabularnewline
Are there overlapping or derivative organisations? & CQ8 & \texttt{lack:derivedFrom} / \texttt{lack:hasDerivation} \tabularnewline
What is the reach of a given actor's network? & CQ9 & \texttt{lack:associatedWith} (inferred) \tabularnewline
How do actor networks change over time? & CQ10 & \texttt{lack:since} / \texttt{lack:until} (reification) \tabularnewline
When were key actors and organisations active? & CQ11 & \texttt{lack:activeSince} / \texttt{lack:activeUntil} \tabularnewline
Who has moved between organisations? & CQ10 + CQ5 & \texttt{lack:employedBy} + temporal reification \tabularnewline
\hline
\end{tabular}
\end{table}

%\subsubsection{Methodology}

\paragraph{Methodology} For each competency question, we report the number of triples for the relevant relation(s) before and after inferencing, as derived from the KG statistics. We also report the number of distinct entities affected, obtained by running SPARQL queries against the ClimateSense endpoint (\url{https://sparql.climatesense.kmi.tools/climatesense}, graph \texttt{<https://purl.net/climatesense/lack>}). Coverage is classified into three tiers: \textbf{Strong} (more than 5,000 triples), \textbf{Moderate} (between 1,000 and 5,000 triples), and \textbf{Weak} (fewer than 1,000 triples). For competency questions involving temporal annotation (CQ10, CQ11), coverage depends on the proportion of entities and relations decorated with \texttt{lack:activeSince}/\texttt{lack:activeUntil} or with \texttt{lack:since}/\texttt{lack:until} on reified statements; these figures are obtained via dedicated SPARQL queries.

% All queries are run against:
% \begin{itemize}
%   \item Endpoint: \url{https://sparql.climatesense.kmi.tools/climatesense}
%   \item Graph: \texttt{<https://purl.net/climatesense/lack>}
% \end{itemize}
%
% \paragraph{CQ2 --- Funding}
% \begin{lstlisting}[language=SPARQL]
% SELECT (COUNT(DISTINCT ?e) AS ?entities)
% FROM <https://purl.net/climatesense/lack>
% WHERE { { ?e <https://purl.net/climatesense/lack/ns#fundedBy> ?o }
%         UNION
%         { ?s <https://purl.net/climatesense/lack/ns#fundedBy> ?e } }
% \end{lstlisting}
%
% \paragraph{CQ3 --- Membership}
% \begin{lstlisting}[language=SPARQL]
% SELECT (COUNT(DISTINCT ?e) AS ?entities)
% FROM <https://purl.net/climatesense/lack>
% WHERE { { ?e <https://purl.net/climatesense/lack/ns#memberOf> ?o }
%         UNION
%         { ?s <https://purl.net/climatesense/lack/ns#memberOf> ?e } }
% \end{lstlisting}
%
% \paragraph{CQ4 --- Leadership}
% \begin{lstlisting}[language=SPARQL]
% SELECT (COUNT(DISTINCT ?e) AS ?entities)
% FROM <https://purl.net/climatesense/lack>
% WHERE { { ?e <https://purl.net/climatesense/lack/ns#leadsAt> ?o }
%         UNION
%         { ?s <https://purl.net/climatesense/lack/ns#leadsAt> ?e } }
% \end{lstlisting}
%
% \paragraph{CQ5 --- Employment}
% \begin{lstlisting}[language=SPARQL]
% SELECT (COUNT(DISTINCT ?e) AS ?entities)
% FROM <https://purl.net/climatesense/lack>
% WHERE { { ?e <https://purl.net/climatesense/lack/ns#employedBy> ?o }
%         UNION
%         { ?s <https://purl.net/climatesense/lack/ns#employedBy> ?e } }
% \end{lstlisting}
%
% \paragraph{CQ6 --- Structural Connections (partnership and sponsorship)}
% \begin{lstlisting}[language=SPARQL]
% SELECT (COUNT(DISTINCT ?e) AS ?entities)
% FROM <https://purl.net/climatesense/lack>
% WHERE { { ?e <https://purl.net/climatesense/lack/ns#hasPartner> ?o }
%         UNION
%         { ?s <https://purl.net/climatesense/lack/ns#hasPartner> ?e }
%         UNION
%         { ?e <https://purl.net/climatesense/lack/ns#sponsored> ?o }
%         UNION
%         { ?s <https://purl.net/climatesense/lack/ns#sponsored> ?e } }
% \end{lstlisting}
%
% \paragraph{CQ7 --- Founding}
% \begin{lstlisting}[language=SPARQL]
% SELECT (COUNT(DISTINCT ?e) AS ?entities)
% FROM <https://purl.net/climatesense/lack>
% WHERE { { ?e <https://purl.net/climatesense/lack/ns#founded> ?o }
%         UNION
%         { ?s <https://purl.net/climatesense/lack/ns#founded> ?e } }
% \end{lstlisting}
%
% \paragraph{CQ8 --- Derivation}
% \begin{lstlisting}[language=SPARQL]
% SELECT (COUNT(DISTINCT ?e) AS ?entities)
% FROM <https://purl.net/climatesense/lack>
% WHERE { { ?e <https://purl.net/climatesense/lack/ns#derivedFrom> ?o }
%         UNION
%         { ?s <https://purl.net/climatesense/lack/ns#derivedFrom> ?e } }
% \end{lstlisting}
%
% \paragraph{CQ9 --- Network Reach}
% \begin{lstlisting}[language=SPARQL]
% SELECT (COUNT(DISTINCT ?e) AS ?entities)
% FROM <https://purl.net/climatesense/lack>
% WHERE {
%     { ?e <https://purl.net/climatesense/lack/ns#associatedWith> ?o }
%     UNION
%     { ?s <https://purl.net/climatesense/lack/ns#associatedWith> ?e }
%     FILTER(STRSTARTS(STR(?e), "https://purl.net/climatesense/lack/entity/"))
% }
% \end{lstlisting}
%
% \paragraph{CQ10 --- Temporal Annotation on Relations}
% \begin{lstlisting}[language=SPARQL]
% SELECT (COUNT(DISTINCT ?stmt) AS ?statements)
% FROM <https://purl.net/climatesense/lack>
% WHERE { ?stmt a <http://www.w3.org/1999/02/22-rdf-syntax-ns#Statement> ;
%               <https://purl.net/climatesense/lack/ns#since> ?since }
% \end{lstlisting}
%
% \paragraph{CQ11 --- Entity-level Temporal Bounds}
% \begin{lstlisting}[language=SPARQL]
% SELECT (COUNT(DISTINCT ?e) AS ?entities)
% FROM <https://purl.net/climatesense/lack>
% WHERE { { ?e <https://purl.net/climatesense/lack/ns#activeSince> ?y }
%         UNION
%         { ?e <https://purl.net/climatesense/lack/ns#activeUntil> ?y } }
% \end{lstlisting}
%
% \paragraph{Coverage Table}

\begin{table}[h]
\centering
\caption{Coverage of competency questions by relation and triple count.}
\label{tab:coverage}
\resizebox{\textwidth}{!}{%
\begin{tabular}{p{0.04\textwidth} p{0.15\textwidth} p{0.2\textwidth} p{0.1\textwidth} p{0.1\textwidth} p{0.1\textwidth} p{0.1\textwidth}}
\hline
\textbf{CQ} & \textbf{RQ (summary)} & \textbf{Relation(s)} & \textbf{Triples (before inf.)} & \textbf{Triples (after inf.)} & \textbf{Affected entities} & \textbf{Coverage} \\
\hline
CQ1  & Who is involved?              & entities                              & 27,974 & 27,974 & 27,974 & Strong \\
CQ2  & How are actors funded?        & \texttt{fundedBy} / \texttt{hasFunder}       & 5,210  & 10,420 & 3,421  & Strong \\
CQ3  & Who are the members?          & \texttt{memberOf} / \texttt{hasMember}       & 13,469 & 26,912 & 9,718  & Strong \\
CQ4  & Who leads organisations?      & \texttt{leadsAt} / \texttt{hasLeader}        & 5,639  & 11,278 & 6,383  & Strong \\
CQ5  & Employment history?           & \texttt{employedBy} / \texttt{hasEmployee}   & 5,463  & 21,276 & 10,943 & Strong \\
CQ6  & Structural connections?       & \texttt{hasPartner}, \texttt{sponsored}      & 5,686  & 8,013  & 4,365  & Strong \\
CQ7  & Who founded a group?          & \texttt{founded} / \texttt{wasFoundedBy}     & 73     & 146    & 108    & Weak \\
CQ8  & Derivative organisations?     & \texttt{derivedFrom} / \texttt{hasDerivation}& 1,922  & 2,883  & 1,310  & Moderate \\
CQ9  & Network reach?                & \texttt{associatedWith}                      & 3,216  & 91,219 & 26,169 & Strong \\
CQ10 & Networks change over time?    & \texttt{since} / \texttt{until} (reif.)      & ---    & 14,361 stmts & --- & Moderate \\
CQ11 & When were actors active?      & \texttt{activeSince} / \texttt{activeUntil}  & 836    & 836    & 734    & Weak \\
CQ10+CQ5 & Who moved between orgs?  & \texttt{employedBy} + reif.                  & subset of 5,463 & subset of 21,276 & --- & Moderate \\
\hline
\end{tabular}%
}
\end{table}

\paragraph{Discussion}

Coverage is strong across the core transparency and network structure competency questions. Membership, employment, leadership, and funding relations each involve thousands of triples and cover a substantial share of the entity population. The most striking result is the network reach (CQ9): after inferencing, 26,169 out of 27,974 entities --- 93.5\% of the total population --- are reachable via \texttt{associatedWith}, demonstrating that OWL inferencing transforms a sparse set of direct assertions into a near-complete connectivity structure. Employment coverage (CQ5) similarly benefits from inferencing, as leadership triples are promoted via the \texttt{leadsAt} sub-property hierarchy.

Temporal coverage is partial but not negligible: 14,361 reified statements carry \texttt{lack:since} annotations, enabling time-bounded queries over a meaningful subset of relations. Entity-level temporal bounds (\texttt{activeSince}, \texttt{activeUntil}) cover only 734 entities (2.6\%), and should be treated as supplementary rather than comprehensive. Founding relations (CQ7) remain sparse at 108 affected entities, reflecting the difficulty of reliably extracting founding events from the source corpora.

