\section{Knowledge Acquisition}
\label{sec:extraction}
\subsection{Requirements and Competency Questions}
Existing knowledge graphs addressing misinformation and climate communication~\cite{burel2024cimplekg,burel2025climafactskg} typically focus on claims and their veracity, but provide little structured information about the relationships between the actors involved — individuals, organisations, funding ties, and roles over time. 
LACK addresses this gap by representing the relational fabric of the climate-change denial ecosystem.
Defining precise knowledge requirements was a prerequisite for both ontology design and knowledge acquisition. 
Requirements were elicited through a thematic analysis of the primary sources, particularly DeSmog, whose profiles systematically document individuals' and organisations' involvement in climate lobbying. 
Recurring themes identified across profiles include organisational affiliations, employment and leadership roles, funding relationships, and temporal activity spans (often summarised in tables). 
These themes were harmonised into a set of twelve competency questions (CQ1--CQ12), intended to be validated with domain experts, which drove both the ontology engineering process and the extraction pipeline described in the following subsections.

\begin{description}
  \item[\textit{Transparency and Disclosure}]~
  \begin{description}
    \item[CQ1] Which persons and organisations are involved in lobbying against climate science or policy?
    \item[CQ2] Which organisations fund a given person or organisation, and what is the evidence for each funding relationship?
    \item[CQ3] Which persons are members of a given organisation, and during which period?
    \item[CQ4] Who are the leaders of a given organisation, and when did they hold that role?
    \item[CQ5] Which organisations has a given person been employed by, and in what time periods?
  \end{description}
  \item[\textit{Network Structure}]~
  \begin{description}
    \item[CQ6] Which organisations are partners of a given organisation?
    \item[CQ7] Which organisations were founded by a given person or organisation?
    \item[CQ8] Which organisations is a given organisation derived from, or has acquired?
    \item[CQ9] Which persons or organisations are associated with a given entity (direct and indirect connections)?
  \end{description}
  \item[\textit{Temporal Reasoning}]~
  \begin{description}
    \item[CQ10] Which relationships involving a given entity were active during a specific time interval?
    \item[CQ11] Which organisations were active during a given period?
  \end{description}
  \item[\textit{Identity and Deduplication}]~
  \begin{description}
    \item[CQ12] Which entities in the graph refer to the same real-world person or organisation?
  \end{description}
\end{description}

\subsection{Sources}
LACK was built from two complementary web sources, together covering a broad range of actors in the climate lobbying ecosystem.
\textbf{DeSmog Climate Disinformation Database}~\cite{desmog} is a curated, editorially maintained resource profiling individuals and organisations involved in climate science denial and disinformation. 
We collected the profile pages of all entities listed in the database, yielding 943 pages. Profiles typically document an individual's or organisation's positions on climate science, affiliations, funding sources, and public statements.
\textbf{LobbyMap}~\cite{lobbymap}, maintained by InfluenceMap, is the world's leading database of corporate and industry association engagement with climate policy, providing assessments and profiles for approximately 1,000 companies and 330 industry associations. 
We collected profile pages for all entities listed in the LobbyMap Scores analysis (964 pages). 
In addition, a further 338 organisation profiles were collected by following links to organisations referenced within those pages but not themselves included in LobbyMap Scores, yielding 1,302 pages in total\footnote{These data was collected in December 2025.}.
The two sources are complementary in scope: DeSmog focuses primarily on individuals and think tanks involved in active disinformation, while LobbyMap covers corporations and industry associations engaging with climate policy. 
Together, they provide broad coverage of the actors and relationships constituting the climate-change denial ecosystem.
The initial set of pages was collected using SPARQL Anything~\cite{daga2021opinionated}, querying the HTML source of the DeSmog Climate Disinformation Database and the JSON feed underlying the LobbyMap Scores leaderboard table.
\subsection{Extraction of relations from web pages}
The competency questions were translated into a defined set of typed relations between two top-level entity types (Person and Organisation), forming the schema for the extraction pipeline.
Relation extraction was performed by prompting Gemini 2.5 Flash~\cite{gemini25} with a structured prompt applied to each profile page.
The prompt specifies the allowed relation types with their definitions, a strict JSON output schema (a list of \texttt{Relation} objects, each with source, target, relation type, optional temporal annotations as \texttt{xsd:gYear}, a natural language description, and evidence URLs), and constraints requiring the model to use only the provided page as evidence and return valid JSON only.
For DeSmog, page content was fetched directly by the model via Gemini's native URL context tool.
For LobbyMap, HTML pages were fetched separately and passed as input to the model.
The pipeline iterates over all collected profile URLs, invoking the model once per page and storing output as one JSON file per profile, with resumption logic to skip already-processed pages.
After each run, a validation routine identified and deleted malformed or empty outputs; the extraction was then re-run on failed pages, repeating until all pages were successfully processed.

\subsection{Entity Linking}
The relation extraction step produces entities as surface form strings rather than authoritative identifiers, requiring three further operations: deduplication, entity resolution, and linking to Wikidata~\cite{wikidata} — with Wikipedia as a secondary target — or, where no knowledge base entry exists, identification via a dedicated public web page.
The input to this step is a pair of (entity name, evidence link) — the surface form and the source profile page where it appeared — augmented by natural language context sentences aggregated from the extraction step.
The same surface form on the same page is treated as a single entity; the same surface form across different pages is not assumed to refer to the same entity.
A preliminary quality step filters out generic non-entities using Groq-hosted Llama 3.3 70B~\cite{llama33}.
An LLM classifier distinguishes concrete named entities from purely descriptive or quantitative strings, flagging expressions such as \texttt{"14 lobbyists"}, \texttt{"200 civil society groups"}, or \texttt{"Gas lobby"} for removal, while retaining named events, initiatives, and borderline collectives that carry a proper name.
For the remaining entities, we apply a hybrid linking pipeline co-designed with Claude~\cite{claude}, combining Wikidata API candidate retrieval, LLM-based disambiguation, and SPARQL-based verification, with a web search fallback for entities absent from Wikidata.
The pipeline was designed and prototyped using Claude Sonnet 4.6~\cite{claudesonnet46} and executed at scale using Groq-hosted Llama 3.3 70B~\cite{llama33} for cost efficiency.
Candidate Wikidata entries are retrieved via the \texttt{wbsearchentities} API, with a Wikipedia search API fallback for entities not indexed there, resolving article titles to Wikidata QIDs.
Because the \texttt{organisation} type in our data spans a wide range of entity classes — companies, think tanks, PACs, government agencies, events, journals, and coalitions — type-based filtering in Wikidata is unreliable; entity subtype is instead inferred by the LLM from context.
Candidates are passed to the LLM, which selects the best matching QID or returns null, also detecting when a candidate represents a broader parent entity rather than the specific entity itself.
Selected QIDs are verified via SPARQL, retrieving canonical label, Wikipedia sitelink, and parent organisation (via \texttt{P749}/\texttt{P361}).
For entities with no Wikidata match, a web fallback first evaluates the evidence link as a potential primary identifier, then issues an LLM-generated search query via the Google Custom Search API~\cite{googlecse}, with a primary-subject check confirming whether each result page is dedicated to the entity.
The output is an enriched CSV containing Wikidata URIs, Wikipedia URLs, parent entity links, web page fallbacks, and confidence scores, produced at a total cost of approximately \$0.60--0.80 and around four days of processing time.

\subsection{Quality control and error analysis}
\paragraph{Sources} Our collection covers the DeSmog Climate Disinformation Database and the LobbyMap Scores leaderboard in their entirety as of the time of collection, providing complete coverage with respect to these two curated entry points.
With respect to DeSmog, the CDD represents the most systematically curated subset of the broader DeSmog site; other DeSmog databases — covering agribusiness, advertising and PR, and the Koch Network — are relevant to the climate lobbying ecosystem but fall outside the current scope and are left for future work.
With respect to LobbyMap, the Scores leaderboard covers approximately 1,000 companies and 330 industry associations, but InfluenceMap hosts a broader set of content — including sector-level reports, country profiles, and policy engagement assessments — that was not included in the current collection.
Extending coverage to these additional sources remains an important direction for future work.
\paragraph{Relations}

Relation extraction was evaluated on a sample of 300 relations drawn from 8 DeSmog profile pages.
Three annotators (the authors) worked in pairs, each pair covering approximately 100 relations, with disagreements resolved by discussion.
Each relation was assessed on three dimensions: truthfulness (is the relation supported by the source page?), validity (is the relation type and its domain and range correctly applied according to the schema?), and temporal correctness (are the temporal annotations accurate?).

Truthfulness accuracy is 0.93 (0.99 with partial credit), validity 0.907 (0.95 with partial), and temporal correctness 0.797 (0.91 with partial), where partial credit captures approximately correct extractions.

The main source of truthfulness errors is the conflation of specific sub-roles with the coarser schema relations: the model frequently uses \texttt{is president of} or \texttt{is director of} where the source text indicates a more specific role such as vice-president, deputy director, or departmental director.
These cases will be addressed during ontology refinement and KG construction, where finer-grained role distinctions can be introduced.
A recurrent validity issue is the misapplication of organisation-level relations to person-organisation pairs: for example, \texttt{has partner} was used when a person holds a partner title at a law or consulting firm, whereas the relation was intended to connect two organisations in a formal partnership.
This reflects an ambiguity in the original relation schema that has since been refined.
Temporal correctness is the weakest dimension, with errors arising from missing dates, incorrect inference of date ranges, and ambiguity in encoding point-in-time vs.\ interval information.

This evaluation covers DeSmog extractions only, which we acknowledge as a limitation.
LobbyMap was not formally evaluated; however, an informal review of a sample of LobbyMap extractions — whose pages share the same HTML structure and similar tabular layout as DeSmog profiles — suggested comparable extraction quality.

\paragraph{Entities}

Entity linking was evaluated on a sample of 225 entities annotated by four annotators (the authors), each covering approximately 56 entities, with a subset supervised by a second annotator and disagreements resolved by discussion.
Each entity was assessed on five dimensions: entity subtype correctness, Wikidata URI, Wikipedia URL, parent entity, and web page (where applicable); see-also links were assessed separately.

Entity subtype accuracy is 0.951, Wikidata URI 0.920, Wikipedia URL 0.909, and web page 0.938, indicating that the pipeline reliably identifies and links entities across all primary output fields.
Parent entity is the weakest dimension at 0.718; errors appear in part to stem from cases where the pipeline assigned a stock exchange as the parent organisation of publicly listed companies, an artefact of how Wikidata encodes P749/P361 relations.
See-also links achieved perfect accuracy across all annotators.
Of the 275 entities with see-also content, 25 included at least one novel URL beyond the evidence link, contributing 55 additional reference pages in total.

% \todo{NIL entities: Report the proportion of entities for which no external identifier (Wikidata, Wikipedia, web page) was found, and discuss implications for reusability and completeness.}
Of the 27,945 entities in the KG, 10,189 (36.5\%) are linked to Wikidata or DBpedia, while 17,756 (63.5\%) remain without an external identifier --- a proportion that is consistent across both sources: 64.4\% of DeSmog-only entities and 65.7\% of LobbyMap-only entities are NIL.
This high NIL rate is not a pipeline failure but a domain characteristic: the climate lobbying ecosystem is densely populated with minor think tank staff, obscure industry consultants, short-lived coalitions, and regional trade bodies that are simply not represented in general-purpose knowledge bases such as Wikidata.
By contrast, entities appearing in both sources --- those prominent enough to be independently documented by DeSmog and LobbyMap --- are linked at a rate of 95.7\% (488 out of 510), confirming that the pipeline reliably identifies well-known actors.
NIL entities are resolvable within the KG via their LACK URI and retain their label and source provenance; web page and parent entity fields, captured during entity linking but not yet promoted to \texttt{owl:sameAs} assertions, offer a path to further grounding and are left to future work.

A total of 29 entities appear with inconsistent type assignments across source 
pages --- annotated as \texttt{lack:Person} in some pages and 
\texttt{lack:Collective} in others --- a known data quality issue arising from the LLM extraction pipeline assigning types independently per page, to be resolved in a future release.
