\section{Introduction}
\label{sec:introduction}

\paragraph{Background and Motivation.}
Efforts to address climate change are systematically hindered by organised campaigns aimed at undermining public trust in climate science and delaying effective policy action~\cite{oreskes2011merchants}.
A growing ecosystem of investigative journalists, fact-checkers, and civil society organisations --- including DeSmog\footnote{\url{https://www.desmog.com/}}, InfluenceMap/LobbyMap\footnote{\url{https://lobbymap.org/}}, and SourceWatch\footnote{\url{https://www.sourcewatch.org/}} --- monitors and documents the individuals and organisations driving these campaigns, supporting tasks such as tracing funding flows, mapping organisational networks, and assessing whether actors' public positions align with scientific consensus.
Despite the breadth of this work, information across these sources remains siloed, heterogeneous in format, and difficult to query or analyse computationally at scale.
This paper presents work carried out within the ClimateSense project~\cite{climatesense}, which builds tools to monitor and analyse climate misinformation across geospatial, temporal, and topical dimensions.
What is missing is a structured, interlinked, machine-readable resource integrating information about climate lobbying actors and their relationships --- one that can support both human investigators and automated analysis pipelines.

\paragraph{Problem Description.}
Consider an investigative journalist seeking to understand the network behind a prominent climate sceptic think tank: who funds it, who sits on its board, which staff have previously worked for fossil fuel companies, and whether those individuals are linked to other lobbying groups.
The information needed exists --- spread across DeSmog, LobbyMap, and Wikidata --- but in incompatible formats, organised around different entity models, and not linked across sources, making even this single question require hours of manual cross-referencing.
The problem is compounded by the temporal dimension: people move between organisations, funding arrangements begin and end, and front groups are created and dissolved --- often around key events such as COP summits or legislative votes --- yet existing sources rarely capture this dynamic structure in a queryable form.
What is needed is a semantically structured resource that makes relationships between actors explicit, typed, and temporally grounded --- enabling queries such as \emph{who was funding this organisation between 2015 and 2020?} or \emph{which individuals have moved between the fossil fuel industry and climate policy advocacy?}

\paragraph{Proposed Solution.}
We present LACK (Lobbying Against Climate Knowledge), a knowledge graph of persons and organisations involved in lobbying against climate science and policy, together with the typed, temporally annotated relationships between them.
LACK is constructed from two large investigative corpora --- 943 profile pages from DeSmog and over 1,300 entries from LobbyMap/InfluenceMap --- from which approximately 70,000 relations are extracted automatically using a large language model pipeline guided by a purpose-built lightweight ontology.
Entities are linked to Wikidata, enabling cross-source deduplication and enrichment with biographical, sectoral, and geographic context.
The resource is published following FAIR principles, with a persistent URI, an open licence (CC BY 4.0), and a machine-readable ontology description.
Beyond direct investigative queries, LACK is designed to support complex analytical tasks such as network centrality analysis, community detection, and theme propagation across actor networks, as demonstrated in the use case presented in Section~\ref{sec:usecase}.

\paragraph{Contributions.}
This paper makes the following contributions:
\begin{itemize}
    \item The \textbf{LACK ontology}, a purpose-built OWL vocabulary covering the key relation types in the climate lobbying domain, developed following ontology engineering best practices and reusing established vocabularies where appropriate.
    \item The \textbf{LACK knowledge graph}, comprising approximately 70,000 typed, temporally annotated relations between persons and organisations, extracted from DeSmog and LobbyMap/InfluenceMap, linked to Wikidata, and published as Linked Open Data under a CC BY 4.0 licence at a persistent URI following FAIR principles.
    \item An \textbf{LLM-based relation extraction pipeline}, a reusable and evaluated method for extracting typed, temporally annotated relations from investigative journalism text.
    \item An \textbf{evaluation with domain experts} from the investigative journalism and climate accountability sector, assessing the utility and value of the resource for real-world investigative tasks.
    \item A \textbf{sustainability and maintenance plan}, situating LACK within the ongoing ClimateSense project~\cite{climatesense} and committing to continued updates as source corpora expand.
\end{itemize}

\paragraph{Paper Structure.}
The remainder of this paper is structured as follows.
Section~\ref{sec:related} reviews related work on knowledge graphs for investigative research and climate misinformation.
Section~\ref{sec:extraction} describes the knowledge extraction pipeline.
Section~\ref{sec:ontology} presents the LACK ontology.
Section~\ref{sec:construction} describes the construction of the knowledge graph.
Section~\ref{sec:usecase} illustrates the analytical potential of the resource through a use case scenario.
Section~\ref{sec:evaluation} reports on the evaluation of the extraction pipeline and the assessment of the resource with domain experts.
Section~\ref{sec:resource} provides the resource description, including availability, licence, and sustainability plan.
Section~\ref{sec:conclusion} concludes and outlines directions for future work.
