\section{Background and Related Work}
\label{sec:related}

Organised efforts to obstruct climate science and delay policy action are extensively
documented by a growing ecosystem of investigative platforms.
DeSmog~\cite{desmog} maintains a database of profiles of individuals and organisations
involved in climate science denial and fossil fuel lobbying; LobbyMap~\cite{lobbymap}
tracks corporate engagement with climate policy across hundreds of companies and
industry groups; SourceWatch catalogues front groups, think tanks, and their funding
relationships.
The scale and persistence of these campaigns have been analysed in depth by Oreskes
and Conway~\cite{oreskes2011merchants}, whose work documents the deliberate strategies
used to manufacture doubt about scientific consensus.
Despite the breadth and rigour of the investigative work these platforms represent,
the information they produce remains heterogeneous in format, siloed across sources,
and not interlinked in a way that supports computational analysis at scale.
Related efforts in the Semantic Web community have begun to address the broader
problem of climate misinformation through structured resources: CimpleKG~\cite{burel2024cimplekg}
is a continuously updated knowledge graph linking misinformation claims, fact-checks,
and contextual factors; ClimaFactsKG~\cite{burel2025climafactskg} focuses on
interlinking scientific evidence to support the rebuttal of climate misinformation.
These resources are complementary to LACK rather than directly comparable: they are
oriented towards claim verification and scientific evidence, whereas the domain of
climate lobbying --- the networks of persons and organisations working to influence
policy --- remains without a structured, machine-readable representation.

Knowledge graphs have been increasingly adopted as infrastructure for investigative
journalism and news analytics.
Opdahl et al.~\cite{opdahl2022survey} provide a comprehensive review of semantic
knowledge graph applications across the full news production pipeline, identifying
actor network analysis and background knowledge enrichment as key but underserved
use cases.
Gallofr\'e Oca\~na and Opdahl~\cite{gallofre2022jkp} survey fourteen journalistic
knowledge platforms in research and practice, finding that while metadata annotation
and event monitoring are well supported, deeper investigative tasks --- such as tracing
funding relationships or reconstructing organisational histories --- remain largely
unaddressed.
Berven et al.~\cite{berven2020kg} describe a concrete platform combining knowledge
graphs, NLP, and machine learning to support newsroom workflows, demonstrating the
practical viability of KG-based investigative infrastructure.
At the level of knowledge representation, Alexander et al.~\cite{alexander2023manifesto}
demonstrate KG construction from a journalistic archive, and Motta et
al.~\cite{motta2025epistemology} develop an ontology-driven framework for structured
news content representation, illustrating how formal models can underpin large-scale
media analytics.
Collectively, this body of work establishes the value of knowledge graphs for
journalism, but focuses primarily on news content annotation and event extraction
rather than on the domain of political and corporate actor networks as a primary
investigative resource.

The construction of LACK draws on recent advances in LLM-based knowledge graph
construction and relation extraction.
Trajanoska et al.~\cite{trajanoska2023llmkg} demonstrate that large language models
can drive automated KG construction from unstructured text, outperforming specialised
models on joint entity and relation extraction tasks.
Papaluca et al.~\cite{papaluca2024zeroshot} show that LLMs are competitive with
fully trained baselines for triplet extraction in zero- and few-shot settings,
particularly when prompted with contextual information retrieved from an existing
knowledge base.
For the heterogeneous web sources from which LACK is constructed, the
Fa\c{c}ade-X~\cite{asprino2023knowledge} approach and its SPARQL~Anything
implementation~\cite{daga2021opinionated} provide a principled method for unified
KG construction across structurally diverse inputs.
Ontology design follows established reuse practices, drawing on
Schema.org~\cite{schemaorg}, PROV-O~\cite{provo}, and DCMI terms~\cite{dcterms}
for provenance and metadata, and Wikidata~\cite{wikidata} as the backbone for
entity linking.
The resource is published following the FAIR principles~\cite{wilkinson2016fair},
ensuring findability, accessibility, interoperability, and reusability.

Taken together, the existing landscape reveals a clear gap: investigative platforms
document climate lobbying actors and their relationships in depth, but in formats
that resist computational analysis; journalism knowledge graphs support news
analytics but not the domain of political influence networks; and while LLM-based
KG construction methods are maturing rapidly, they have not been applied to the
climate accountability domain.
A structured, typed, temporally annotated, and Wikidata-linked knowledge graph of
lobbying actors and relationships --- built via an evaluated extraction pipeline and
published as Linked Open Data --- would address all three dimensions of this gap,
and is precisely what the remainder of this paper describes.