\section{Use Cases}
\label{sec:usecase}

The following case studies illustrate connections that emerge from LACK's integration of multiple independent sources. Each case follows the same structure: two statements, each drawn from a different source — the Desmog Climate Disinformation Database and LobbyMap — share a common entity that acts as a bridge. Neither source mentions the entities cited in the other --- yet their combination, through the shared bridge entity, reveals a relationship that no single source makes visible.

% NOTE: This section requires \usepackage{listings} and \usepackage{tikz} in main.tex
% The graph figure (Figure~\ref{fig:cs-bp}) could be moved to supplementary material
% if page budget is tight. The SPARQL listing could likewise move to supplementary.

\section{Use Cases}
\label{sec:usecase}

The following case studies illustrate connections that emerge from LACK's integration of multiple independent sources. Each case follows the same structure: two statements, each drawn from a different source — the DeSmog Climate Disinformation Database and LobbyMap — share a common entity that acts as a bridge. Neither source mentions the entities cited in the other — yet their combination, through the shared bridge entity, reveals a relationship that no single source makes visible. The connections revealed are structural, derived from publicly available data; they do not imply wrongdoing, shared intent, or direct collaboration, and should be treated as research leads rather than evidential claims.

%-----------------------------------------------------------------------
\subsection*{Case 1: Darren Woods $\rightarrow$ Exxon $\rightarrow$ Heartland Institute}

\noindent\textbf{Source A (InfluenceMap):} Darren Woods \texttt{lack:leadsAt} Exxon.\\
\textbf{Source B (DeSmog):} Exxon \texttt{lack:sponsored} Heartland Institute.\\
\textbf{Bridge entity:} Exxon.

\smallskip
\noindent InfluenceMap documents Darren Woods as leading Exxon, while DeSmog records Exxon as a sponsor of the Heartland Institute, a think tank prominently associated with climate science denial. Neither source references the other's entity: InfluenceMap does not mention the Heartland Institute, and DeSmog does not mention Woods. LACK makes the chain explicit, linking a named corporate officer to a disinformation-adjacent organisation through his employer.

\smallskip
\noindent The SPARQL query in Listing~\ref{lst:sparql-cs1} generalises this pattern, retrieving all persons in LACK who lead an organisation that has sponsored another entity.

\begin{lstlisting}[
  caption={SPARQL query retrieving all persons who lead an organisation
           that has sponsored another entity.},
  label={lst:sparql-cs1},
  basicstyle=\ttfamily\small,
  frame=single,
  breaklines=true
]
PREFIX lack: <https://purl.net/climatesense/lack/ns#>

SELECT ?person ?org ?target
FROM <https://purl.net/climatesense/lack>
WHERE {
  ?person  lack:leadsAt   ?org .
  ?org     lack:sponsored ?target .
}
\end{lstlisting}

%-----------------------------------------------------------------------
\subsection*{Case 2: Cambridge Analytica $\rightarrow$ BP $\rightarrow$ Business Council of Australia}

\noindent\textbf{Source A (DeSmog):} Cambridge Analytica \texttt{lack:hasPartner} BP.\\
\textbf{Source B (InfluenceMap):} BP \texttt{lack:memberOf} Business Council of Australia.\\
\textbf{Bridge entity:} BP.

\smallskip
\noindent DeSmog records a partnership between Cambridge Analytica, the data and political consultancy firm, and BP. InfluenceMap separately documents BP's membership of the Business Council of Australia, an industry body with a documented record of opposing climate legislation. The two facts originate from different investigative contexts — one focused on political data operations, the other on fossil fuel industry lobbying in Australia — and share only BP as a common entity. Their integration in LACK surfaces a cross-domain, cross-jurisdictional structural connection that neither source makes visible on its own.

\smallskip
\noindent Figure~\ref{fig:cs-bp} shows the graph representation of this two-hop path as it appears in LACK.

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[
      entity/.style={draw, rounded corners=3pt, fill=gray!10,
                     text width=3cm, align=center, font=\small},
      every edge/.style={draw, ->, >=stealth, font=\footnotesize}
    ]
    \node[entity] (ca)  {Cambridge\\Analytica};
    \node[entity] (bp)  [right=1.2cm of ca]  {BP};
    \node[entity] (bca) [right=1.2cm of bp]  {Business Council\\of Australia};

    \draw (ca)  edge[bend left=15]  node[above] {\texttt{hasPartner}} (bp);
    \draw (bp)  edge[bend left=15]  node[above] {\texttt{memberOf}}   (bca);

    \node[font=\scriptsize, text=gray, below=0.15cm of ca]  {DeSmog};
    \node[font=\scriptsize, text=gray, below=0.15cm of bca] {InfluenceMap};
  \end{tikzpicture}
  \caption{Two-hop path connecting Cambridge Analytica to the Business Council
           of Australia via BP, integrating statements from DeSmog and
           InfluenceMap. Source annotations indicate the origin of each
           endpoint statement; BP is the bridge entity present in both sources.}
  \label{fig:cs-bp}
\end{figure}

%-----------------------------------------------------------------------
\subsection*{Case 3: Nick Stavropoulos $\rightarrow$ PG\&E $\rightarrow$ ZETA}

\noindent\textbf{Source A (DeSmog):} Nick Stavropoulos \texttt{lack:leadsAt} PG\&E.\\
\textbf{Source B (LobbyMap):} PG\&E \texttt{lack:memberOf} Zero Emission Transportation Association (ZETA).\\
\textbf{Bridge entity:} PG\&E.

\smallskip
\noindent DeSmog profiles Nick Stavropoulos as an executive at PG\&E, the Californian utility. LobbyMap independently records PG\&E's membership of the Zero Emission Transportation Association, an electric vehicle industry coalition. Unlike the preceding cases, the target organisation here is not associated with climate denial; ZETA actively advocates for EV adoption. This case illustrates that LACK captures the full complexity of influence networks — including actors whose affiliations span both fossil fuel infrastructure and clean energy advocacy — rather than mapping only clear-cut disinformation actors.
